---
title: "Movie Night"
author: "Kelly Thackeray, Judy Camarena"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
 
```

```{r echo = F, message=FALSE, warning=FALSE}
library(tidyverse)
library('knitr')
#library('quantreg')
Movie_1000 <- read_csv('Highest_Holywood_Grossing_Movies.csv')
My_imdb <- read_csv('imdb_top_1000.csv')
My_imdb$Released_Year <- as.numeric(My_imdb$Released_Year)
Movie_1000$`Budget (in $)`<- as.numeric(Movie_1000$`Budget (in $)`)
Movie_1000$`Domestic Sales (in $)`<- as.numeric(Movie_1000$`Domestic Sales (in $)`)
Movie_1000$`Domestisc Opening (in $)` <- as.numeric(Movie_1000$`Domestic Opening (in $)`)

My_imdb <- My_imdb %>% 
  mutate(Runtime = str_split_i(Runtime, pattern = " ", 1),
         Runtime = as.numeric(Runtime), 
         Released_Year = as.numeric(Released_Year))

#movie_data <- full_join(Movie_1000, My_imdb, join_by("Title" == "Series_Title")) %>% arrange(Title)
movie_data_inner <- inner_join(Movie_1000, My_imdb, join_by("Title" == "Series_Title")) %>% filter(Released_Year >= 1994) %>% na.omit()


movie_data_inner <- rename(movie_data_inner,'domestic_sales' = 'Domestic Sales (in $)')
movie_data_inner <- rename(movie_data_inner,'international_sales' = 'International Sales (in $)')
movie_data_inner <- rename(movie_data_inner, 'budget' = 'Budget (in $)')
movie_data_inner <- rename(movie_data_inner, 'domestic_opening' = 'Domestic Opening (in $)')
movie_data_inner <- rename(movie_data_inner, 'world_wide_sales' ='World Wide Sales (in $)')
movie_data_inner$domestic_opening <- as.numeric(movie_data_inner$domestic_opening)

#glimpse(movie_data_inner)


```

### Introduction

The datasets used for this report are CSV files from Kaggle named IMDB Movie dataset from and Highest_Holywood_Grossing_Movies. The datasets reflect movie sales.

The links to the data imdb_top_1000.csv and Highest_Holywood_Grossing_Movies.csv

------------------------------------------------------------------------

### Problem Statement and Questions

To understand movie industry sales trends and the role distributors play.

-   Which countries were in the top ten most frequently?
-   Sales per release year; domestic and international
-   World wide sales to budget
-   Domestic sales to budget
-   Interntational sales to budget
-   Domestic vs international sales
-   Opening weekend vs total sales correlation

#### Distributor

-   Worldwide sales per distributor
-   Top 10 sales per year per distributor
-   Top directors per distributor
-   Lowest sales of distributors

------------------------------------------------------------------------

We can begin by examining an overview with this chart and graph.

#### Number of Movies Released Over the Last 30 Years per Year

```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}
#movie_data_inner %>% group_by(Year,Released_Year) %>% summarise(n =n()) %>% arrange(-n) %>% 
  #na.omit()

released <- movie_data_inner %>% 
  group_by(Released_Year) %>%  
  summarise(Count = n()) %>% 
  arrange(-Count) %>% 
  na.omit()

library(kableExtra)
kable(released, col.names = c('Year Released', 'Movies'))%>%  
  kable_styling(full_width = F, position = "center")
```

It is indicated that 2009, 2010, and 2014 released the most movies per year.

```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}
movie_data_inner %>% ggplot(aes(x = Released_Year)) + geom_histogram()+
labs(title = 'Movies Released per Year', x = 'Year Released', y = 'Number of Movies')

```

------------------------------------------------------------------------

***Now that we know what years released the most movies, we wanted to plot domestic and international sales yearly. We were expecting the data to show us the same trends.***

***


```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}

movie_data_inner %>% 
  ggplot()+
  aes(domestic_sales, international_sales, color = Released_Year)+
  geom_point(na.rm = TRUE, alpha = .5)+
  labs(title = 'Sales According to Release Year', x = 'Domestic Sales', y = 'International Sales')
```

The data told a different story.

------------------------------------------------------------------------

We investigated further by only looking into domestic sales.

```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}
movie_data_inner %>% 
  ggplot() +
  aes(x = Released_Year,
      y = domestic_sales) +
  geom_col(na.rm = TRUE)+
  labs(title = 'Domestic Sales by Release Year', x = 'Year Released', y = 'Domestic Sales')
```

Interestingly, 2009 was the highest-grossing year in domestic sales, followed by 2013, even though we had the most movie releases in 2012.

------------------------------------------------------------------------

When we took a look at international sales...

***
#### International Sales
```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}
movie_data_inner %>% 
  ggplot() +
  aes(x = Released_Year,
      y = international_sales) +
  geom_col(na.rm = TRUE)+
  labs(title = 'International Sales by Release Year', x = 'Year Released', y = 'International Sales')
```

The data showed 2014 and 2009 as the most lucrative year in sales.

------------------------------------------------------------------------

Noting the difference in movie release years versus the highest-grossing years prompted us to look into sales per budget.

```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}
movie_data_inner %>% 
  ggplot()+
  aes(domestic_sales, international_sales, color = budget)+
  geom_point(na.rm = TRUE, alpha = .5, color = 'red')+
  labs(title = 'Correlation of World Wide Sales to Budget', x = 'Domestic Sales', y = 'International Sales' )
```

------------------------------------------------------------------------

We decided to look more closely into domestic sales and budgets to identify trends.

#### Domestic sales and budget
```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}
movie_data_inner %>% 
  ggplot() +
  aes(x = budget,
      y = domestic_sales) +
  geom_point(na.rm = TRUE, alpha = .5, color = 'red')+
  labs(title = 'Correlation of Domestic Sales to Budget', x = 'Budget', y = 'Domestic Sales' )
```

Our findings suggest that a specific budget range could be identified as a strategic goal for the industry. While there were some outliers, the data indicated that there is no need to exceed the budget to achieve higher sales.

------------------------------------------------------------------------

When we plotted the same data for international sales and budgets similar conclusions were reached.

#### International Sales and Budget

```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}
movie_data_inner %>% 
  ggplot() +
  aes(x = budget,
      y = international_sales) +
  geom_point(na.rm = TRUE, alpha = .5, color = 'red')+
  labs(title = 'Correlation of International Sales to Budget', x = 'Budget', y = 'International Sales' )

```

------------------------------------------------------------------------

Next, we wanted to compare domestic sales to international sales.

```{r echo = F, message=FALSE, fig.align='center', warning=FALSE}
movie_data_inner %>% 
  ggplot() +
  aes(x = domestic_sales,
      y = international_sales) +
  geom_smooth(na.rm = TRUE) +
  labs(title = 'How Do International Sales Compare to Domestic Sales', x = 'Domestic Sales', y =   'International Sales')

sales_kabble <- movie_data_inner %>% select(Title, domestic_sales, international_sales) %>% head(10)

kable(sales_kabble, col.names = c('Movie Name','Domestic Sales',' International sales'))


## Correlation Opening Weekend and Total Sales

movie_data_inner %>% 
  ggplot()+
  aes(domestic_opening,domestic_sales)+
  geom_point(na.rm = TRUE, alpha = .5, color = 'red') +
  labs(title = 'Opening Weekend vs. Total Sales', x = 'Domestic Opening', y = 'Domestic Sales' )
  
```

------------------------------------------------------------------------

Movies depend on their distribution. So, we wanted to identify our largest distributor.

#### Distribution

```{r echo = F, message=FALSE, fig.align='center', warning=FALSE}
movie_data_inner %>% select(world_wide_sales,Distributor) %>% 
  ggplot()+
  aes(world_wide_sales, y = reorder(Distributor, world_wide_sales, sum))+
  geom_col()+
  labs(title = 'World Wide Sales Per Distributor',x='World Wide Sales', y= 'Distributor')
```

We concluded that Walt Disney Studios was our largest worldwide distributor.

------------------------------------------------------------------------

We wanted to know which year each distributor had reported the highest sales. To narrow our search, we limited the dataset to only list the top 10 sales.

#### Top 10 Sales per Year per Distributor

```{r echo = F, message=FALSE,fig.align='center', warning=FALSE}
highest_sales_per_year <- movie_data_inner %>% select(Distributor,Released_Year, world_wide_sales) %>% group_by(Distributor) %>% arrange(-Released_Year, -world_wide_sales) %>% head(10)
  
kable(highest_sales_per_year, col.names = c('Distributor','Year Released','Total Sales'))
```

Walt Disney and other distributors showed their most profitable year in 2019.

------------------------------------------------------------------------

As we tried to identify what could make a movie more profitable, we decided to look at the top directors per distributor. We wanted to know how many movies each director produced and who they used as their distributor.

#### Top Directors per Distributor

```{r echo = F, message=FALSE, fig.width=11,fig.align='center', warning=FALSE}
movie_data_inner %>% group_by(Director) %>% head(10) %>% 
  ggplot()+
  aes(Director, fill = Distributor)+
  geom_bar()+
  labs(title = 'Top 10 Directors Per Distributor', y= 'Number of Movies Directed')


```

It was unsurprising to find Anthony Russo, who used Walt Disney Studios as his distributor, directing most of the films. James Cameron came in second, using Twenty Century Fox and Paramount Pictures to distribute his films.

------------------------------------------------------------------------

## Lowest Sales of Distributors

```{r echo = F, message=FALSE, fig.align='center', warning=FALSE}

movie_data_inner %>% tail(10)%>% 
  ggplot(aes(world_wide_sales, color = Distributor)) + 
  geom_density()+
  labs(title = 'Lowest 10 Sales by Distributor',x='World Wide Sales')
  
```

------------------------------------------------------------------------

### Summary

In our analysis, we found that the number of movies released in the year will not directly indicate a high grossing year in movie sales both internationally or domestically. We also concluded that staying within the budget is the most financially beneficial practice since being over budget did not correlate to higher grossing sales. The number of films a director produces is as significant as who they use to distribute the film. Walt Disney Studios has the farthest reach; therefore, it is an excellent option for distribution.

It is important to consider that the data did not measure or account for numerous factors beyond anyone's control, like weather, social, or economic factors that have impacted movie sales.

