---
title: "Movie Night"
author: "Kelly Thackeray, Judy Camarena"
date: "`r Sys.Date()`"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
 
```

```{r echo = F, message=FALSE, warning=FALSE}
library(tidyverse)
library('knitr')
#library('quantreg')
Movie_1000 <- read_csv('Highest_Holywood_Grossing_Movies.csv')
My_imdb <- read_csv('imdb_top_1000.csv')
My_imdb$Released_Year <- as.numeric(My_imdb$Released_Year)
Movie_1000$`Budget (in $)`<- as.numeric(Movie_1000$`Budget (in $)`)
Movie_1000$`Domestic Sales (in $)`<- as.numeric(Movie_1000$`Domestic Sales (in $)`)
Movie_1000$`Domestisc Opening (in $)` <- as.numeric(Movie_1000$`Domestic Opening (in $)`)

My_imdb <- My_imdb %>% 
  mutate(Runtime = str_split_i(Runtime, pattern = " ", 1),
         Runtime = as.numeric(Runtime), 
         Released_Year = as.numeric(Released_Year))

#movie_data <- full_join(Movie_1000, My_imdb, join_by("Title" == "Series_Title")) %>% arrange(Title)
movie_data_inner <- inner_join(Movie_1000, My_imdb, join_by("Title" == "Series_Title")) %>% filter(Released_Year >= 1994) %>% na.omit()


movie_data_inner <- rename(movie_data_inner,'domestic_sales' = 'Domestic Sales (in $)')
movie_data_inner <- rename(movie_data_inner,'international_sales' = 'International Sales (in $)')
movie_data_inner <- rename(movie_data_inner, 'budget' = 'Budget (in $)')
movie_data_inner <- rename(movie_data_inner, 'domestic_opening' = 'Domestic Opening (in $)')
movie_data_inner <- rename(movie_data_inner, 'world_wide_sales' ='World Wide Sales (in $)')
movie_data_inner$domestic_opening <- as.numeric(movie_data_inner$domestic_opening)

#glimpse(movie_data_inner)


```

---

Number of Movies Released Over the Last 30 Years per Year
---
```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}
#movie_data_inner %>% group_by(Year,Released_Year) %>% summarise(n =n()) %>% arrange(-n) %>% 
  #na.omit()

released <- movie_data_inner %>% 
  group_by(Released_Year) %>%  
  summarise(Count = n()) %>% 
  arrange(-Count) %>% 
  na.omit()

library(kableExtra)
kable(released, col.names = c('Year Released', 'Movies'))%>%  
  kable_styling(full_width = F, position = "center")
```


```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}
movie_data_inner %>% ggplot(aes(x = Released_Year)) + geom_histogram()+
labs(title = 'Movies Released per Year', x = 'Year Released', y = 'Number of Movies')

```

---

Sales per Release Year
---
```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}

movie_data_inner %>% 
  ggplot()+
  aes(domestic_sales, international_sales, color = Released_Year)+
  geom_point(na.rm = TRUE, alpha = .5)+
  labs(title = 'Sales According to Release Year', x = 'Domestic Sales', y = 'International Sales')
```

---

Domestic Sales
---
```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}
movie_data_inner %>% 
  ggplot() +
  aes(x = Released_Year,
      y = domestic_sales) +
  geom_col(na.rm = TRUE)+
  labs(title = 'Domestic Sales by Release Year', x = 'Year Released', y = 'Domestic Sales')
```

---

International Sales
---
```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}
movie_data_inner %>% 
  ggplot() +
  aes(x = Released_Year,
      y = international_sales) +
  geom_col(na.rm = TRUE)+
  labs(title = 'International Sales by Release Year', x = 'Year Released', y = 'International Sales')
```

---

Sales per Budget
---
```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}
movie_data_inner %>% 
  ggplot()+
  aes(domestic_sales, international_sales, color = budget)+
  geom_point(na.rm = TRUE, alpha = .5, color = 'red')+
  labs(title = 'Correlation of World Wide Sales to Budget', x = 'Domestic Sales', y = 'International Sales' )
```

---

Domestic Sales and Budget
---
```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}
movie_data_inner %>% 
  ggplot() +
  aes(x = budget,
      y = domestic_sales) +
  geom_point(na.rm = TRUE, alpha = .5, color = 'red')+
  labs(title = 'Correlation of Domestic Sales to Budget', x = 'Budget', y = 'Domestic Sales' )
```

---

International Sales and Budget
---
```{r echo = F, message=FALSE, fig.align='center',warning=FALSE}
movie_data_inner %>% 
  ggplot() +
  aes(x = budget,
      y = international_sales) +
  geom_point(na.rm = TRUE, alpha = .5, color = 'red')+
  labs(title = 'Correlation of International Sales to Budget', x = 'Budget', y = 'International Sales' )

```

---

Domestic vs. International Sales
---
```{r echo = F, message=FALSE, fig.align='center', warning=FALSE}
movie_data_inner %>% 
  ggplot() +
  aes(x = domestic_sales,
      y = international_sales) +
  geom_smooth(na.rm = TRUE) +
  labs(title = 'How Do International Sales Compare to Domestic Sales', x = 'Domestic Sales', y =   'International Sales')

sales_kabble <- movie_data_inner %>% select(Title, domestic_sales, international_sales) %>% head(10)

kable(sales_kabble, col.names = c('Movie Name','Domestic Sales',' International sales'))
```


---

Correlation Opening Weekend and Total Sales
---
```{r echo = F, message=FALSE, fig.align='center', warning=FALSE}
movie_data_inner %>% 
  ggplot()+
  aes(domestic_opening,domestic_sales)+
  geom_point(na.rm = TRUE, alpha = .5, color = 'red') +
  labs(title = 'Opening Weekend vs. Total Sales', x = 'Domestic Opening', y = 'Domestic Sales' )
  
```


---

Distribution
---
```{r echo = F, message=FALSE, fig.align='center', warning=FALSE}
movie_data_inner %>% select(world_wide_sales,Distributor) %>% 
  ggplot()+
  aes(world_wide_sales, y = reorder(Distributor, world_wide_sales, sum))+
  geom_col()+
  labs(title = 'World Wide Sales Per Distributor',x='World Wide Sales', y= 'Distributor')
```


---

Top 10 Sales per Year per Distributor
---
```{r echo = F, message=FALSE,fig.align='center', warning=FALSE}
highest_sales_per_year <- movie_data_inner %>% select(Distributor,Released_Year, world_wide_sales) %>% group_by(Distributor) %>% arrange(-Released_Year, -world_wide_sales) %>% head(10)
  
kable(highest_sales_per_year, col.names = c('Distributor','Year Released','Total Sales'))
```

---

Top Directors per Distributor
---
```{r echo = F, message=FALSE, fig.width=11,fig.align='center', warning=FALSE}
movie_data_inner %>% group_by(Director) %>% head(10) %>% 
  ggplot()+
  aes(Director, fill = Distributor)+
  geom_bar()+
  labs(title = 'Top 10 Directors Per Distributor', y= 'Number of Movies Directed')


```



---

Lowest Sales of Distributors
---
```{r echo = F, message=FALSE, fig.align='center', warning=FALSE}

movie_data_inner %>% tail(10)%>% 
  ggplot(aes(world_wide_sales, color = Distributor)) + 
  geom_density()+
  labs(title = 'Lowest 10 Sales by Distributor',x='World Wide Sales')
  
```
